Dynein project log

### 2016-12-23 thesis_stuff/thesis_stuff.tex
Remove bad dG calculation.

\begin{align*}
  k_{bind} &= Ae^{-\beta(\Delta G_{bind} + \Delta G_{conf})}\\
  k_{bind} &= \left(Ae^{-\beta\Delta G_{bind}}\right)e^{-\beta\Delta G_{conf}}\\
  k_{bind} &= Be^{-\beta\Delta G_{conf})}\hspace{2cm}\mbox{B constant at constant T}\\
  \left<k_{bind}\right> &= \left<Be^{-\beta\Delta G_{conf}}\right>\\
  \left<k_{bind}\right> &= Be^{-\beta\Delta \left<G_{conf}\right>}\\
  \left<\Delta G_{conf}\right> &= \frac{1}{2}k_BT = \frac12\beta^{-1}\\
  \left<k_{bind}\right> &= Be^{-1/2}\\
  \rightarrow B &= \frac{k_{bind}}{\sqrt{e}}
\end{align*}

@@

\begin{equation*}
  B = \frac{k_{b}}{n\sqrt{e}}
\end{equation*}

@@

>>>>

\begin{align*}
  k_{bind} &= Ae^{-\beta(\Delta G_{bind} + \Delta G_{conf})}\\
  k_{bind} &= \left(Ae^{-\beta\Delta G_{bind}}\right)e^{-\beta\Delta G_{conf}}\\
  k_{bind} &= Be^{-\beta\Delta G_{conf})}\hspace{2cm}\mbox{B constant at constant T}\\
  \left<k_{bind}\right> &= \left<Be^{-\beta\Delta G_{conf}}\right>\\
  \left<k_{bind}\right> &= Be^{-\beta\Delta \left<G_{conf}\right>}\\
  \left<\Delta G_{conf}\right> &= \frac{1}{2}k_BT = \frac12\beta^{-1}\hspace{2cm}\mbox{David, what was the justification for this again?}\\
  \left<k_{bind}\right> &= Be^{-1/2}\\
  \rightarrow B &= k_{bind}\sqrt{e}
\end{align*}

@@

\begin{equation*}
  B = \frac{k_{b}\sqrt{e}}{n}
\end{equation*}

@@

\subsection{ATP Concentration from Weihong's Paper}
Weihong says in the Supplemental Methods section that the ATP concentration of the ``dynein motility buffer'' used to take his videos was 1mM, with no added ADP or Pi.
